Association between trauma severity models and opportunities for improvement:

### 2022-11-29 manuscript.Rmd
results plots

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  pdf_document: default
  html_document:
    df_print: paged
    number_sections: true
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pt
linestretch: 1
always_allow_html: yes
editor_options: 
   chunk_output_type: inline
---

@@

```{r main, echo=FALSE, message = FALSE}
  source("main.R") 
```

@@

```{r, echo=FALSE, out.width = "400px"}
## knitr::include_graphics("images/ofi.png") ## ofi_diagram.R; save_png(ofi_diagram(), "ofi") to update
```

@@

RTS, NORMIT and PS12 were computed according to the original published algorithms [@rtsalgorithm; @normit; @psalgorithm]. TRISS was calculated using the revised 2009 coefficients [@triss2010].

@@

```{r, echo=FALSE, out.width = "400px"}
## knitr::include_graphics("images/exclusion.png") ## exclusion_flowchart.R; save_png(exclusion_flowchart(exclusion), "exclusion") to update
```

@@

The median age was `r dd['age']` (IQR: `r dd['age.lo']`-`r dd['age.hi']`). `r dd['male']`% of participants were male. `r dd['blunt']`% of cases were due to blunt force trauma. Of cases where 30-day survival was available, there was a `r dd['mort']`% 30-day mortality rate (`r dd['survival.na']` cases with missing survival data). Of cases where registered data on the highest level of care was available, `r dd['icu']`% had the ICU as their highest level of care (`r dd['care.na']` cases with missing care level data). The median ISS score was `r dd['iss']` (IQR: `r dd['iss.lo']`-`r dd['iss.hi']`).

@@

### TRISS

The odds ratio for TRISS was `r t[['or']]` (95% CI: `r t[['or.ci.lo']]`-`r t[['or.ci.hi']]`, p-value: `r t[['or.p']]`). The ROC is plotted in Figure 3. The AUC for the ROC was `r t[['auc']]` (95% CI: `r t[['auc.ci.lo']]`-`r t[['auc.ci.hi']]`). The integrated calibration index for TRISS was `r t[['ici']]` (95% CI: `r t[['ici.ci']][1]`-`r t[['ici.ci']][2]`. The accuracy curve is shown in Figure 4. The best accuracy was `r t[['acc.max']]` (95% CI: `r t[['acc.ci']][1]`-`r t[['acc.ci']][2]`) and was found at the cutoff `r t[['acc.co']]`.

```{r}
## plot(t[['roc']], main="Fig 3. TRISS Receiver Operating Characteristic Curve.", colorize = TRUE)
```

```{r}
## plot(t[['acc']], main="Fig 4. TRISS Accuracy Curve.")
```

### NORMIT 
The odds ratio for NORMIT was `r n[['or']]` (95% CI: `r n[['or.ci.lo']]`-`r n[['or.ci.hi']]`, p-value: `r n[['or.p']]`). The ROC is plotted in Figure 3. The AUC for the ROC was `r n[['auc']]` (95% CI: `r n[['auc.ci.lo']]`-`r n[['auc.ci.hi']]`). The integrated calibration index for NORMIT was `r n[['ici']]` (95% CI: `r n[['ici.ci']][1]`-`r n[['ici.ci']][2]`. The accuracy curve is shown in Figure 4. The best accuracy was `r n[['acc.max']]` (95% CI: `r n[['acc.ci']][1]`-`r n[['acc.ci']][2]`) and was found at the cutoff `r n[['acc.co']]`.

```{r, echo = FALSE}
## plot(n[['roc']], main="Fig 5. NORMIT Receiver Operating Characteristic Curve.", colorize = TRUE)
```

```{r, echo = FALSE}
## plot(n[['acc']], main="Fig 6. NORMIT Accuracy Curve.")
```

### PS
The odds ratio for PS was `r p[['or']]` (95% CI: `r p[['or.ci.lo']]`-`r p[['or.ci.hi']]`, p-value: `r p[['or.p']]`). The ROC is plotted in Figure 3. The AUC for the ROC was `r p[['auc']]` (95% CI: `r p[['auc.ci.lo']]`-`r p[['auc.ci.hi']]`). The integrated calibration index for PS was `r p[['ici']]` (95% CI: `r p[['ici.ci']][1]`-`r p[['ici.ci']][2]`. The accuracy curve is shown in Figure 4. The best accuracy was `r p[['acc.max']]` (95% CI: `r p[['acc.ci']][1]`-`r p[['acc.ci']][2]`) and was found at the cutoff `r p[['acc.co']]`.

```{r}
## plot(p[['roc']], main="Fig 6. PS Receiver Operating Characteristic Curve.", colorize = TRUE)
```

```{r}
## plot(p[['acc']], main="Fig 7. PS Accuracy Curve.")
```

### Comparison of scores

Table 3 shows a comparison of ?? for the three models analysed.

```{r}
  ### table(results, type = "or.plot")
  ### table(d, type = "deltas")
 ## as_latex(table(d, type = "deltas"))
```

>>>>

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  pdf_document: default
  html_document:
    df_print: paged
    number_sections: true
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pts
linestretch: 1
always_allow_html: yes
editor_options: 
   chunk_output_type: inline
---

@@

```{r main}
  source("main.R") 
```

@@

```{r, echo=FALSE, out.width = "400px"}
knitr::include_graphics("images/ofi.png") ## ofi_diagram.R; save_png(ofi_diagram(), "ofi") to update
```

@@

RTS and PS12 were computed according to the original published algorithms [@rtsalgorithm; @psalgorithm]. NORMIT was calculated with the revised 2018 algorithm [@skagaValidatingPerformanceTRISS2018]. TRISS was calculated using the revised 2009 coefficients [@triss2010].

@@

```{r, echo=FALSE, out.width = "400px"}
knitr::include_graphics("images/exclusion.png") ## exclusion_flowchart.R; save_png(exclusion_flowchart(exclusion), "exclusion") to update
```

@@

The median age was `r dd['age']` (IQR: `r dd['age.lo']`-`r dd['age.hi']`). `r dd['male']`% of participants were male. `r dd['blunt']`% of cases were due to blunt force trauma. The median ISS score was `r dd['iss']` (IQR: `r dd['iss.lo']`-`r dd['iss.hi']`). Of cases where 30-day survival was available, there was a `r dd['mort']`% 30-day mortality rate (`r dd['survival.na']` cases with missing survival data). `r dd['icu']`% of participants received intensive care as their highest level of care.

@@

The fitted curves for the logistic regression models of each score are shown in figure x. The odds ratios for TRISS, NORMIT and PS were `r t[['or']]` (95% CI: `r t[['or.ci.lo']]`-`r t[['or.ci.hi']]`, *p*: `r t[['or.p']]`), `r n[['or']]` (95% CI: `r n[['or.ci.lo']]`-`r n[['or.ci.hi']]`, *p*: `r n[['or.p']]`), and `r p[['or']]` (95% CI: `r p[['or.ci.lo']]`-`r p[['or.ci.hi']]`, *p*: `r p[['or.p']]`) respectively.

```{r}
knitr::include_graphics("images/glm.png") ## update: glm_x3(df)
```

The receiver operating curves for all scores are plotted in figure x. The areas under the curve for TRISS, NORMIT and PS were `r t[['auc']]` (95% CI: `r t[['auc.ci.lo']]`-`r t[['auc.ci.hi']]`), `r n[['auc']]` (95% CI: `r n[['auc.ci.lo']]`-`r n[['auc.ci.hi']]`), and `r p[['auc']]` (95% CI: `r p[['auc.ci.lo']]`-`r p[['auc.ci.hi']]`) respectively.

```{r}
knitr::include_graphics("images/roc.png") ## update: roc_x3(t, n, p)
```

The integrated calibration index for TRISS, NORMIT and PS was `r t[['ici']]` (95% CI: `r t[['ici.ci']][1]`-`r t[['ici.ci']][2]`, `r n[['ici']]` (95% CI: `r n[['ici.ci']][1]`-`r n[['ici.ci']][2]` and `r p[['ici']]` (95% CI: `r p[['ici.ci']][1]`-`r p[['ici.ci']][2]` respectively. The accuracy at all cutoffs is plotted for all scores in figure x. The accuracy at a cutoff of 0.5 for TRISS, NORMIT and PS was `r t[['acc']]` (95% CI: `r t[['acc.ci']][1]`-`r t[['acc.ci']][2]`), `r n[['acc']]` (95% CI: `r n[['acc.ci']][1]`-`r n[['acc.ci']][2]`) and `r p[['acc']]` (95% CI: `r p[['acc.ci']][1]`-`r p[['acc.ci']][2]`) respectively.

```{r}
knitr::include_graphics("images/acc.png") ## update: acc_x3(t, n, p)
```

The differences between the scores for each result are shown in table x.

```{r}
 as_latex(table(d, type = "deltas"))
```
